The Concurrent Calculi Formalisation Benchmark

### 2024-02-07 short-paper/short-paper.tex
start fleshing out the paragraph on coinduction

\paragraph{Coinduction.} \todo{}

>>>>

\paragraph{Coinduction.} \todo{add citations and explain more what the challenge does.}

Coinduction is fundamental to establish properties of processes that
may never terminate, a typical situation. We base our challenge around
bisimulation a coinductively established property for equating the
observed behaviour of potentially infinite processes.

Coinduction is widely supported in proof assistants, Isabelle, Coq,
and Abella seamlessly support coinductive definitions and reasoning.
Agda and Beluga support it through the convenient abstraction
of co-patterns. And newer entrants to the field like the Lean proof
assistant, while not currently available, are working on adding a
notion of coinduction to their system.

As with most features, proof assistants support subtly different
formalisms that enable different techniques and motivate this
challenge. Some systems provide more than one abstraction to use
coinduction. A good example of this are the PACO and interaction tree
libraries for Coq.\todo{Francisco: add citations}.

Common uses for coinduction are to define strong and weak versions of
bisimulation, barbed notions of bisimulation, prove trace equivalence,
etc.

In this challenge we study the notion of strong barbed bisimulation
over a fragment of the $\pi$-calculus.
